---
title: "Project Dashboard"
output-file: index.html
format: 
  dashboard:
    scrolling: true
    embed-resources: true 
    include-in-header:
      text: |
        <style>
        .quarto-dashboard-sidebar {
          background-color: white !important;
          border-right: 1px solid #dee2e6;
        }
        </style>
theme: simplex
---

```{r}
#| label: setup
#| include: false
library(tidyverse)
library(plotly)
library(viridis)


analysis_clean <- read_csv("analysis_clean.csv",show_col_types = FALSE)


analysis_clean <- analysis_clean %>%
  rowwise() %>%
  mutate(privacy_risk = mean(c_across(qid13:qid18), na.rm = TRUE)) %>%
  ungroup() %>%
  mutate(
    ethical_trust_diff = qid28 - qid26,
    trust_group = case_when(
      ethical_trust_diff > 0 ~ "Pro-China ethics",
      ethical_trust_diff < 0 ~ "Pro-US ethics",
      TRUE ~ "Equal trust"
    ),
    # Pre-process Demographics
    gender = factor(
      qid31,
      levels = c(1, 2, 3, 4),
      labels = c("Male", "Female", "Non-binary", "Prefer not to say")
    ),
    age = factor(
      qid32,
      levels = c(1, 2, 3, 4, 5, 6),
      labels = c("Under 18", "18–24", "25–34", "35–44", "45–54", "55 or above")
    ),
    education = factor(
      qid33,
      levels = c(1, 2, 3, 4),
      labels = c("High school or below", "Associate degree", "Bachelor's degree", "Graduate degree or above")
    ),
    income = factor(
      qid35,
      levels = c(1, 2, 3, 4, 5),
      labels = c("≤ $20,000", "$20,001–$49,999", "$50,000–$99,999", "$100,000 or above", "Prefer not to say")
    )
  )

# Calculate summary metrics
n_participants <- nrow(analysis_clean)
age_mode <- names(sort(table(analysis_clean$age), decreasing = TRUE))[1]
gender_mode <- names(sort(table(analysis_clean$gender), decreasing = TRUE))[1]
geo_mode <- names(sort(table(analysis_clean$source), decreasing = TRUE))[1]

```

# Overview

## Sidebar {.sidebar}

**Project Overview**

This study investigates the online community migration of "TikTok Refugees"---users moving from the US-based platform TikTok to the China-based platform RedNote.

Through a structured survey of 130 participants, this research explores cross-platform migration motivations, application usage patterns, and user privacy perceptions.

**Core Research Questions**

-   Demographics & Behavior: What are the demographic characteristics and platform usage behaviors of "TikTok Refugees"?

-   Platform Trust: Do these users exhibit a significant difference in trust between US-based platforms (TikTok) and China-based platforms (RedNote)?

-   Risk Perception: Does a user's risk perception significantly influence their cross-border platform usage behavior?

------------------------------------------------------------------------

## Row {height="110px"}

### Column {width="25%"}

```{r}
#| content: valuebox
#| title: "Total Participants"
list(icon = "people", color = "light", value = n_participants)
```

### Column {width="25%"}

```{r}
#| content: valuebox
#| title: "Primary Age Bracket"
list(icon = "person-badge", color = "light", value = age_mode)
```

### Column {width="25%"}

```{r}
#| content: valuebox
#| title: "Primary Gender"
list(icon = "gender-ambiguous", color = "light", value = gender_mode)
```

### Column {width="25%"}

```{r}
#| content: valuebox
#| title: "Top Region"
list(icon = "globe", color = "light", value = geo_mode)
```

## Row {height="350px"}

### Column {width="1"}

###  {.tabset}

#### Age Distribution

```{r}
#| echo: false
#| message: false
#| warning: false
age_dist <- analysis_clean |> 
  drop_na(age) |>
  count(age, name = "n")

p_age <- ggplot(age_dist, aes(x = fct_rev(age), y = n, fill = age)) +
  geom_col() +
  labs(x = "", y = "Count", title = "Age Distribution") +
  theme_minimal(base_size = 14) +
  theme(legend.position = "none") +
  scale_fill_viridis_d()

ggplotly(p_age, tooltip = c("x", "y")) %>% layout(margin = list(l = 100))
```

#### Gender Distribution

```{r}
#| echo: false
#| message: false
#| warning: false
gender_dist <- analysis_clean |> 
  drop_na(gender) |>
  count(gender, name = "n") |> 
  mutate(gender = reorder(gender, n))

p_gender <- ggplot(gender_dist, aes(x = gender, y= n, fill = gender)) +
  geom_col() +
  labs(x = "", y = "Count", title = "Gender Distribution") +
  theme_minimal(base_size = 14) +
  theme(legend.position = "none") +
  scale_fill_viridis_d(option = "magma")

ggplotly(p_gender, tooltip = c("x", "y")) %>% layout(margin = list(l = 100))
```

#### Geographic Distribution

```{r}
#| echo: false
#| message: false
#| warning: false
geo_dist <- analysis_clean |> 
  drop_na(source) |>
  count(source, name = "n") |> 
  mutate(source = reorder(source, n))

p_geo <- ggplot(geo_dist, aes(x = source, y= n, fill = source)) +
  geom_col() +
  labs(x = "", y = "Count", title = "Geographic Distribution") +
  theme_minimal(base_size = 14) +
  theme(legend.position = "none") +
  scale_fill_viridis_d(option = "turbo")

ggplotly(p_geo, tooltip = c("x", "y")) %>% layout(margin = list(l = 100))
```

#### Education Level

```{r}
#| echo: false
#| message: false
#| warning: false
edu_dist <- analysis_clean |> 
  drop_na(education) |>
  count(education, name = "n")

p_edu <- ggplot(edu_dist, aes(x = education, y = n, fill = education)) +
  geom_col() +
  labs(x = "", y = "Count", title = "Education Level") +
  theme_minimal(base_size = 14) +
  theme(legend.position = "none", axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_viridis_d(option = "plasma")

ggplotly(p_edu, tooltip = c("x", "y")) %>% layout(margin = list(b = 120))
```

#### Income Level

```{r}
#| echo: false
#| message: false
#| warning: false
inc_dist <- analysis_clean |> 
  drop_na(income) |>
  count(income, name = "n")

p_inc <- ggplot(inc_dist, aes(x = income, y = n, fill = income)) +
  geom_col() +
  labs(x = "", y = "Count", title = "Income Level") +
  theme_minimal(base_size = 14) +
  theme(legend.position = "none", axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_viridis_d(option = "cividis")

ggplotly(p_inc, tooltip = c("x", "y")) %>% layout(margin = list(b = 120))
```

