---
title: "Project Dashboard"
output-file: dashboard.html
format: 
  dashboard:
    orientation: rows
    scrolling: true
    embed-resources: true
    theme: [cosmo, custom.scss]
    nav-buttons:
      - icon: house
        text: Home
        href: home.html
---

```{r}
#| label: setup
#| include: false
library(tidyverse)
library(plotly)
library(viridis)

analysis_clean <- read_csv("analysis_clean.csv", col_types = cols(qid8 = col_character(), qid9 = col_character()), show_col_types = FALSE)

analysis_clean <- analysis_clean %>%
  rowwise() %>%
  mutate(privacy_risk = mean(c_across(qid13:qid18), na.rm = TRUE)) %>%
  ungroup() %>%
  mutate(
    ethical_trust_diff = qid28 - qid26,
    trust_group = case_when(
      ethical_trust_diff > 0 ~ "Pro-China ethics",
      ethical_trust_diff < 0 ~ "Pro-US ethics",
      TRUE ~ "Equal trust"
    ),
    # Pre-process Demographics
    gender = factor(
      qid31,
      levels = c(1, 2, 3, 4),
      labels = c("Male", "Female", "Non-binary", "Prefer not to say")
    ),
    age = factor(
      qid32,
      levels = c(1, 2, 3, 4, 5, 6),
      labels = c("Under 18", "18-24", "25-34", "35-44", "45-54", "55 or above")
    ),
    education = factor(
      qid33,
      levels = c(1, 2, 3, 4),
      labels = c("High school or below", "Associate degree", "Bachelor's degree", "Graduate degree or above")
    ),
    income = factor(
      qid35,
      levels = c(1, 2, 3, 4, 5),
      labels = c("<= $20,000", "$20,001-$49,999", "$50,000-$99,999", "$100,000 or above", "Prefer not to say")
    ),
    # Pre-process Platform Usage
    tiktok_before = factor(
      qid3,
      levels = c(1, 2, 3, 4),
      labels = c("Rarely", "A few times per week", "Daily", "Multiple times a day")
    ),
    rednote_now = factor(
      qid4,
      levels = c(1, 2, 3, 4),
      labels = c("Rarely", "A few times per week", "Daily", "Multiple times a day")
    ),
    tiktok_after = factor(
      qid6,
      levels = c(1, 2, 3, 4),
      labels = c("Yes, regularly", "Yes, decreased", "Rarely now", "Stopped using it")
    )
  )


activities_dict <- c(
  "1" = "Browsing content",
  "2" = "Posting content",
  "3" = "Interacting with others",
  "4" = "Shopping",
  "5" = "Other Activity"
)

reasons_dict <- c(
  "1" = "Similar US platforms unavailable",
  "2" = "Better content alignment",
  "3" = "Encouraged by friends/influencers",
  "4" = "Bypass U.S. restrictions",
  "5" = "Access unique products/services",
  "6" = "Curiosity about Chinese platforms",
  "7" = "Information outside US media",
  "8" = "Connect to international communities",
  "9" = "Other Reason"
)
n_participants <- nrow(analysis_clean)
age_mode <- names(sort(table(analysis_clean$age), decreasing = TRUE))[1]
gender_mode <- names(sort(table(analysis_clean$gender), decreasing = TRUE))[1]
geo_mode <- names(sort(table(analysis_clean$source), decreasing = TRUE))[1]

# High-end designer palette available globally
prof_palette_1 <- c("#264653", "#2A9D8F", "#E9C46A", "#F4A261", "#E76F51", "#8AB17D", "#BABB74", "#D8A47F", "#F28482", "#F5CAC3", "#84A59D", "#F6BD60")
```

# Sidebar {.sidebar}

**Project Overview**

This study investigates the online community migration of "TikTok Refugees"---users moving from the US-based platform TikTok to the China-based platform RedNote.

Through a structured survey of 130 participants, this research explores cross-platform migration motivations, application usage patterns, and user privacy perceptions.

**Research Background**

These news highlights the phenomenon of "TikTok refugees" migrating to RedNote:

* [Over half a million ‘TikTok refugees’ flock to China's RedNote](https://www.reuters.com/technology/over-half-million-tiktok-refugees-flock-chinas-rednote-2025-01-14/)
* [TikTok users flock to Chinese app RedNote as US ban looms](https://www.bbc.com/news/articles/c2475l7zpqyo)
* [What to know about RedNote, the Chinese app that American TikTokkers are flooding](https://www.npr.org/2025/01/15/nx-s1-5260742/tiktok-china-rednote-xiaohongshu-app)

**Core Research Questions**

1.  Demographics & Behavior: What are the demographic characteristics and platform usage behaviors of "TikTok Refugees"?

2.  Platform Trust: Do these users exhibit a significant difference in trust between US-based platforms (TikTok) and China-based platforms (RedNote)?

3.  Risk Perception: Does a user's risk perception significantly influence their cross-border platform usage behavior?

# Demographics

## Row {height="150px"}

###  {width="25%"}

```{r}
#| content: valuebox
#| title: "Migrating Users Surveyed"
list(icon = "people-fill", color = "light", value = n_participants)
```

###  {width="25%"}

```{r}
#| content: valuebox
#| title: "Dominant Age Cohort"
list(icon = "person-lines-fill", color = "light", value = age_mode)
```

###  {width="25%"}

```{r}
#| content: valuebox
#| title: "Primary Gender Identity"
list(icon = "person-badge-fill", color = "light", value = gender_mode)
```

###  {width="25%"}

```{r}
#| content: valuebox
#| title: "Geographic Concentration"
list(icon = "globe-americas", color = "light", value = geo_mode)
```

## Row {height="50%"}

```{r}
#| echo: false
#| message: false
#| warning: false
#| title: "Age and Gender Pyramid"

df_pyramid <- analysis_clean |> 
  select(Age = age, Gender = gender) |> 
  drop_na(Age, Gender) |> 
  mutate(Age = fct_drop(Age)) |>
  count(Age, Gender) |> 
  mutate(
    n_pyramid = if_else(Gender == "Male", -n, as.numeric(n)),
    hover_text = paste("Gender: ", Gender, "<br>Count: ", n, sep = "")
  )


gender_palette <- c("Male" = "#3B5BA5", "Female" = "#E07A9A", "Non-binary" = "#8E7DBE", "Prefer not to say" = "#BDBDBD")

p_pyramid <- ggplot(df_pyramid, aes(x = Age, y = n_pyramid, fill = Gender, text = hover_text)) +
  geom_col(alpha = 0.9, width = 0.8) +
  coord_flip() +
  scale_y_continuous(labels = abs) +
  theme_minimal(base_size = 14, base_family = "sans") +
  labs(x = "Age Group", y = "Number of Users") +
  theme(
    legend.position = "bottom",
    legend.title = element_blank(),
    panel.grid.minor = element_blank(),
    axis.text = element_text(color = "#4a4a4a")
  ) +
  scale_fill_manual(values = gender_palette)

ggplotly(p_pyramid, tooltip = "text") %>%
  layout(margin = list(b = 60), barmode = 'relative') %>%
  config(displayModeBar = FALSE)
```

## Row {height="50%"}

```{r}
#| echo: false
#| message: false
#| warning: false
#| title: "Region Distribution"

df_reg <- analysis_clean |> 
  count(Region = source) |> 
  drop_na(Region)

p_reg <- ggplot(df_reg, aes(x = Region, y = n, fill = Region)) +
  geom_col(alpha = 0.9, width = 0.75) +
  labs(x = "Region", y = "Users", fill = "Region") +
  theme_minimal(base_size = 12, base_family = "sans") +
  theme(
    axis.text.x = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank()
  ) +
  scale_fill_manual(values = colorRampPalette(c("#36506C", "#5D85A6", "#8EB4C6", "#D1E2EE"))(nrow(df_reg)))

ggplotly(p_reg, tooltip = c("x", "y")) %>% 
  layout(
    legend = list(orientation = "v", x = 1, y = 0.5, bgcolor = "rgba(255,255,255,0.7)"),
    margin = list(b = 40, r = 120)
  ) %>%
  config(displayModeBar = FALSE)
```

```{r}
#| echo: false
#| message: false
#| warning: false
#| title: "Education Distribution"

df_edu <- analysis_clean |> 
  count(Education = education) |> 
  drop_na(Education)

p_edu <- ggplot(df_edu, aes(x = Education, y = n, fill = Education)) +
  geom_col(alpha = 0.9, width = 0.75) +
  labs(x = "Education Level", y = "Users", fill = "Education") +
  theme_minimal(base_size = 12, base_family = "sans") +
  theme(
    axis.text.x = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank()
  ) +
  scale_fill_manual(values = colorRampPalette(c("#487968", "#7AA288", "#ADC7AD", "#DFE9DD"))(nrow(df_edu)))

ggplotly(p_edu, tooltip = c("x", "y")) %>% 
  layout(
    legend = list(orientation = "v", x = 1, y = 0.5, bgcolor = "rgba(255,255,255,0.7)"),
    margin = list(b = 40, r = 120)
  ) %>%
  config(displayModeBar = FALSE)
```

```{r}
#| echo: false
#| message: false
#| warning: false
#| title: "Income Distribution"

df_inc <- analysis_clean |> 
  count(Income = income) |> 
  drop_na(Income)

p_inc <- ggplot(df_inc, aes(x = Income, y = n, fill = Income)) +
  geom_col(alpha = 0.9, width = 0.75) +
  labs(x = "Income Bracket", y = "Users", fill = "Income") +
  theme_minimal(base_size = 12, base_family = "sans") +
  theme(
    axis.text.x = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank()
  ) +
  scale_fill_manual(values = colorRampPalette(c("#8A677B", "#B8909D", "#DCBABC", "#F3DFD8", "#FDF1E9"))(nrow(df_inc)))

ggplotly(p_inc, tooltip = c("x", "y")) %>% 
  layout(
    legend = list(orientation = "v", x = 1, y = 0.5, bgcolor = "rgba(255,255,255,0.7)"),
    margin = list(b = 40, r = 120)
  ) %>%
  config(displayModeBar = FALSE)
```

# Platform Behaviors

## Row {height="55%"}

```{r}
#| echo: false
#| message: false
#| warning: false
#| title: "User Journey: Motivation to Activity to Frequency"

activities_dict <- c("1" = "Browsing content", "2" = "Posting content", "3" = "Interacting with others", "4" = "Shopping", "5" = "Other Activity")
reasons_dict <- c("1" = "Similar US platforms unavailable", "2" = "Better content alignment", "3" = "Encouraged by friends/influencers", "4" = "Bypass U.S. restrictions", "5" = "Access unique products/services", "6" = "Curiosity about Chinese platforms", "7" = "Information outside US media", "8" = "Connect to international communities", "9" = "Other Reason")

# Expand data for Sankey
flow_df <- analysis_clean %>%
  select(id = qid1, qid9, qid8, Frequency = qid6) %>%
  drop_na() %>%
  separate_longer_delim(qid9, delim = ",") %>%
  mutate(Reason = reasons_dict[str_trim(qid9)]) %>%
  separate_longer_delim(qid8, delim = ",") %>%
  mutate(Activity = activities_dict[str_trim(qid8)]) %>%
  mutate(Frequency = factor(Frequency, levels = c(1, 2, 3, 4), labels = c("Rarely", "A few times per week", "Daily", "Multiple times a day")))

s_nodes <- unique(c(as.character(flow_df$Reason), as.character(flow_df$Activity), as.character(flow_df$Frequency))) %>% na.omit()

s_links <- bind_rows(
  flow_df %>% count(source = Reason, target = Activity) %>% rename(value = n),
  flow_df %>% count(source = Activity, target = as.character(Frequency)) %>% rename(value = n)
) %>%
  mutate(source_id = match(source, s_nodes) - 1, target_id = match(target, s_nodes) - 1)

s_colors <- colorRampPalette(prof_palette_1)(length(s_nodes))

p_behavior_sankey_best <- plot_ly(
    type = "sankey",
    orientation = "h",
    node = list(
      label = s_nodes,
      pad = 15,
      thickness = 25,
      line = list(color = "#ffffff", width = 1),
      color = s_colors
    ),
    link = list(
      source = s_links$source_id,
      target = s_links$target_id,
      value = s_links$value,
      color = "rgba(120, 120, 120, 0.1)"  
    )
  ) %>% 
  layout(
    margin = list(t = 60, b = 30, l = 30, r = 30),
    font = list(family = "sans", size = 11, color = "#4a4a4a"),
    plot_bgcolor = "#ffffff",
    paper_bgcolor = "#ffffff",
    annotations = list(
      list(x = 0, y = 1.05, text = "Motivation", showarrow = FALSE, font = list(size = 14, color = "#1d3557", family="sans"), xref = "paper", yref = "paper"),
      list(x = 0.5, y = 1.05, text = "Activity", showarrow = FALSE, font = list(size = 14, color = "#1d3557", family="sans"), xref = "paper", yref = "paper"),
      list(x = 1, y = 1.05, text = "Usage Frequency", showarrow = FALSE, font = list(size = 14, color = "#1d3557", family="sans"), xref = "paper", yref = "paper")
    )
  ) %>%
  config(displayModeBar = FALSE)

p_behavior_sankey_best
```

## Row {.tabset height="45%"}

```{r}
#| echo: false
#| message: false
#| warning: false
#| title: "Reasons for Using RedNote"
# Process QID9
reasons_df <- analysis_clean |> 
  select(qid9) |> 
  drop_na() |> 
  separate_longer_delim(qid9, delim = ",") |> 
  mutate(Reason = reasons_dict[str_trim(qid9)]) |> 
  count(Reason, name = "n") |> 
  mutate(Reason = reorder(Reason, n))


reason_sankey_palette <- c(
  "Similar US platforms unavailable" = "#E87552",
  "Better content alignment" = "#264653",
  "Encouraged by friends/influencers" = "#B59269",
  "Bypass U.S. restrictions" = "#317874",
  "Access unique products/services" = "#93B27B",
  "Curiosity about Chinese platforms" = "#62A884",
  "Information outside US media" = "#DDC16C",
  "Connect to international communities" = "#F0B064",
  "Other Reason" = "#F0955D"
)

p_reas_best <- ggplot(reasons_df, aes(x = Reason, y = n, fill = Reason)) +
  geom_col(alpha = 0.9, width = 0.75) +
  coord_flip() +
  labs(x = "", y = "Number of Selections", title = "Why are users moving to RedNote?") +
  theme_minimal(base_size = 14, base_family = "sans") +
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 15, color = "#2c3e50"),
    panel.grid.major.y = element_blank(),
    panel.grid.minor = element_blank()
  ) +
  scale_fill_manual(values = reason_sankey_palette)

ggplotly(p_reas_best, tooltip = c("x", "y")) %>% 
  config(displayModeBar = FALSE) %>%
  layout(margin = list(t = 40, b = 20, l = 250, r = 20))
```

```{r}
#| echo: false
#| message: false
#| warning: false
#| title: "Primary Activities on RedNote"
# Process QID8
activities_df <- analysis_clean |> 
  select(qid8) |> 
  drop_na() |> 
  separate_longer_delim(qid8, delim = ",") |> 
  mutate(Activity = activities_dict[str_trim(qid8)]) |> 
  count(Activity, name = "n") |> 
  mutate(Activity = reorder(Activity, n))


act_sankey_palette <- c(
  "Browsing content" = "#9DA86C",
  "Posting content" = "#E48179",
  "Interacting with others" = "#BEA764",
  "Shopping" = "#D88A79",
  "Other Activity" = "#C98662"
)

p_act_best <- ggplot(activities_df, aes(x = Activity, y = n, fill = Activity)) +
  geom_col(alpha = 0.9, width = 0.7) +
  coord_flip() +
  labs(x = "", y = "Number of Selections", title = "What are users doing on RedNote?") +
  theme_minimal(base_size = 14, base_family = "sans") +
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 15, color = "#2c3e50"),
    panel.grid.major.y = element_blank(),
    panel.grid.minor = element_blank()
  ) +
  scale_fill_manual(values = act_sankey_palette)

ggplotly(p_act_best, tooltip = c("x", "y")) %>% 
  config(displayModeBar = FALSE) %>%
  layout(margin = list(t = 40, b = 20, l = 200, r = 20))
```

```{r}
#| echo: false
#| message: false
#| warning: false
#| title: "RedNote Usage Frequency"
df_rn <- analysis_clean |> 
  select(Response = rednote_now) |> 
  drop_na() |> 
  count(Response) |> 
  mutate(
    Response = factor(Response, levels = c(
      "Multiple times a day", "Daily", "A few times per week", "Rarely"
    ))
  )

freq_sankey_palette <- c(
  "Rarely" = "#A5A973",
  "A few times per week" = "#F3B654",
  "Daily" = "#E7BFB7",
  "Multiple times a day" = "#9FA7A3"
)

p_comp_best <- ggplot(df_rn, aes(x = Response, y = n, fill = Response)) +
  geom_col(alpha = 0.95, width = 0.6) +
  labs(x = "", y = "Number of Users") +
  theme_minimal(base_size = 14, base_family = "sans") +
  theme(
    legend.position = "none",
    axis.text.x = element_text(angle = 45, hjust = 1, size = 11, color = "#2D2D2D"),
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank()
  ) +
  scale_fill_manual(values = freq_sankey_palette)

ggplotly(p_comp_best, tooltip = c("x", "y")) %>% 
  config(displayModeBar = FALSE) %>%
  layout(margin = list(t = 40, b = 80, l = 20, r = 20))
```

# Trust Analysis
::: {.callout-note}
## Measurement note
This section uses two constructed variables. 

1. **Ethical trust difference** is derived from two 1–5 Likert-scale items: *“I trust US-based platforms more than Chinese platforms in terms of ethical standards”* and *“I trust China-based platforms more than US-based platforms in terms of ethical standards.”* The score is calculated as **China-trust minus US-trust**. Positive values indicate relatively greater trust in China-based platforms, negative values indicate relatively greater trust in US-based platforms, and zero indicates equal trust.


2. **Perceived privacy risk** is measured as the mean of six 1–5 Likert-scale items about RedNote, covering hesitation to share personal information, concern about secondary use without consent, concern about sharing with third parties or governments, desire to access collected data, lack of control over data use, and concern that inaccurate data may cause harm. Higher values indicate greater perceived privacy risk.
:::
## Row {height="600px" layout-ncol="1"}

```{r}
#| echo: false
#| message: false
#| warning: false
#| title: "Participants’ Ethical Trust Skews Toward China"

df_hist <- analysis_clean %>% drop_na(ethical_trust_diff, trust_group)


best_trust_palette <- c("Pro-China ethics" = "#d62828", "Pro-US ethics" = "#003049", "Equal trust" = "grey70")

p_hist_best <- ggplot(df_hist, aes(x = ethical_trust_diff, fill = trust_group)) +
  geom_histogram(bins = 20, color = "white", alpha = 0.9, linewidth = 0.5) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "#333333", linewidth = 1) +
  scale_fill_manual(values = best_trust_palette) +
  labs(
    x = "Ethical Trust Difference (China − US)",
    y = "Respondents Count",
    fill = "Orientation",
    subtitle = "Higher values indicate stronger trust in Chinese platform ethics over US ones"
  ) +
  theme_minimal(base_size = 14, base_family = "sans") +
  theme(
    legend.position = "right",
    panel.grid.minor = element_blank()
  ) +
  annotate("text", x = 2, y = max(table(cut(df_hist$ethical_trust_diff, breaks=20))), 
           label = "Pro-China Trust", color = "#d62828", fontface = "bold", hjust = 0) +
  annotate("text", x = -2, y = max(table(cut(df_hist$ethical_trust_diff, breaks=20))), 
           label = "Pro-US Trust", color = "#003049", fontface = "bold", hjust = 1)

ggplotly(p_hist_best) %>%
  layout(margin = list(t = 40, b = 40, l = 50))
```

```{r}
#| echo: false
#| message: false
#| warning: false
#| title: "Higher Ethical Trust in China Corresponds to Lower Perceived Privacy Risk"

df_scatter <- analysis_clean %>% drop_na(ethical_trust_diff, privacy_risk)

p_scatter_best <- ggplot(df_scatter, aes(x = ethical_trust_diff, y = privacy_risk)) +
  geom_point(alpha = 0.8, size = 2.5, aes(color = trust_group, text = paste("Trust Diff:", ethical_trust_diff, "<br>Privacy Risk:", round(privacy_risk, 2)))) +
  geom_smooth(method = "lm", se = TRUE, color = "#333333", linewidth = 0.8, fill = "#e5e5e5") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "#888888") +
  scale_color_manual(values = best_trust_palette) +
  labs(
    x = "Ethical Trust Difference (China − US)",
    y = "Perceived Privacy Risk on RedNote",
    color = "Orientation",
    subtitle = "Negative correlation indicates users trusting American platforms are more wary of RedNote"
  ) +
  theme_minimal(base_size = 14, base_family = "sans") +
  theme(
    legend.position = "none",
    panel.grid.minor = element_blank()
  )

ggplotly(p_scatter_best, tooltip = "text") %>%
  layout(margin = list(t = 40, b = 40, l = 50))
```
