---
title: "Project Dashboard"
output-file: index.html
format: 
  dashboard:
    orientation: rows
    scrolling: true
    embed-resources: true
    theme: [cosmo, custom.scss]
---

```{r}
#| label: setup
#| include: false
library(tidyverse)
library(plotly)
library(viridis)

analysis_clean <- read_csv("analysis_clean.csv", col_types = cols(qid8 = col_character(), qid9 = col_character()), show_col_types = FALSE)

analysis_clean <- analysis_clean %>%
  rowwise() %>%
  mutate(privacy_risk = mean(c_across(qid13:qid18), na.rm = TRUE)) %>%
  ungroup() %>%
  mutate(
    ethical_trust_diff = qid28 - qid26,
    trust_group = case_when(
      ethical_trust_diff > 0 ~ "Pro-China ethics",
      ethical_trust_diff < 0 ~ "Pro-US ethics",
      TRUE ~ "Equal trust"
    ),
    # Pre-process Demographics
    gender = factor(
      qid31,
      levels = c(1, 2, 3, 4),
      labels = c("Male", "Female", "Non-binary", "Prefer not to say")
    ),
    age = factor(
      qid32,
      levels = c(1, 2, 3, 4, 5, 6),
      labels = c("Under 18", "18-24", "25-34", "35-44", "45-54", "55 or above")
    ),
    education = factor(
      qid33,
      levels = c(1, 2, 3, 4),
      labels = c("High school or below", "Associate degree", "Bachelor's degree", "Graduate degree or above")
    ),
    income = factor(
      qid35,
      levels = c(1, 2, 3, 4, 5),
      labels = c("<= $20,000", "$20,001-$49,999", "$50,000-$99,999", "$100,000 or above", "Prefer not to say")
    ),
    # Pre-process Platform Usage
    tiktok_before = factor(
      qid3,
      levels = c(1, 2, 3, 4),
      labels = c("Rarely", "A few times per week", "Daily", "Multiple times a day")
    ),
    rednote_now = factor(
      qid4,
      levels = c(1, 2, 3, 4),
      labels = c("Rarely", "A few times per week", "Daily", "Multiple times a day")
    ),
    tiktok_after = factor(
      qid6,
      levels = c(1, 2, 3, 4),
      labels = c("Yes, regularly", "Yes, decreased", "Rarely now", "Stopped using it")
    )
  )


activities_dict <- c(
  "1" = "Browsing content",
  "2" = "Posting content",
  "3" = "Interacting with others",
  "4" = "Shopping",
  "5" = "Other Activity"
)

reasons_dict <- c(
  "1" = "Similar US platforms unavailable",
  "2" = "Better content alignment",
  "3" = "Encouraged by friends/influencers",
  "4" = "Bypass U.S. restrictions",
  "5" = "Access unique products/services",
  "6" = "Curiosity about Chinese platforms",
  "7" = "Information outside US media",
  "8" = "Connect to international communities",
  "9" = "Other Reason"
)
n_participants <- nrow(analysis_clean)
age_mode <- names(sort(table(analysis_clean$age), decreasing = TRUE))[1]
gender_mode <- names(sort(table(analysis_clean$gender), decreasing = TRUE))[1]
geo_mode <- names(sort(table(analysis_clean$source), decreasing = TRUE))[1]

# High-end designer palette available globally
prof_palette_1 <- c("#264653", "#2A9D8F", "#E9C46A", "#F4A261", "#E76F51", "#8AB17D", "#BABB74", "#D8A47F", "#F28482", "#F5CAC3", "#84A59D", "#F6BD60")
```

# Sidebar {.sidebar}

**Project Overview**

This study investigates the online community migration of "TikTok Refugees"---users moving from the US-based platform TikTok to the China-based platform RedNote.

Through a structured survey of 130 participants, this research explores cross-platform migration motivations, application usage patterns, and user privacy perceptions.

**Research Background**

These news highlights the phenomenon of "TikTok refugees" migrating to RedNote:

* [Over half a million ‘TikTok refugees’ flock to China's RedNote](https://www.reuters.com/technology/over-half-million-tiktok-refugees-flock-chinas-rednote-2025-01-14/)
* [TikTok users flock to Chinese app RedNote as US ban looms](https://www.bbc.com/news/articles/c2475l7zpqyo)
* [What to know about RedNote, the Chinese app that American TikTokkers are flooding](https://www.npr.org/2025/01/15/nx-s1-5260742/tiktok-china-rednote-xiaohongshu-app)

**Core Research Questions**

1.  Demographics & Behavior: What are the demographic characteristics and platform usage behaviors of "TikTok Refugees"?

2.  Platform Trust: Do these users exhibit a significant difference in trust between US-based platforms (TikTok) and China-based platforms (RedNote)?

3.  Risk Perception: Does a user's risk perception significantly influence their cross-border platform usage behavior?

# Demographics

## Row {height="150px"}

###  {width="25%"}

```{r}
#| content: valuebox
#| title: "Migrating Users Surveyed"
list(icon = "people-fill", color = "white", value = n_participants)
```

###  {width="25%"}

```{r}
#| content: valuebox
#| title: "Dominant Age Cohort"
list(icon = "person-lines-fill", color = "white", value = age_mode)
```

###  {width="25%"}

```{r}
#| content: valuebox
#| title: "Primary Gender Identity"
list(icon = "person-badge-fill", color = "white", value = gender_mode)
```

###  {width="25%"}

```{r}
#| content: valuebox
#| title: "Geographic Concentration"
list(icon = "globe-americas", color = "white", value = geo_mode)
```

## Row {.tabset height="500px"}

### Version 1 {layout-ncol="1"}

```{r}
#| echo: false
#| message: false
#| warning: false
#| title: "Demographic Characteristics"
# Combine age, gender, geographic, education, and income
df_demo <- analysis_clean |> 
  select(Age = age, Gender = gender, Region = source, Education = education, Income = income) |> 
  pivot_longer(everything(), names_to = "Demographic", values_to = "Category") |> 
  drop_na(Category) |> 
  count(Demographic, Category)

# We want fixed ordering for categories across panels where possible
# but since they all have different categories, we'll let ggplot handle the ordering via free axes.
# However, to maintain the structural order (like income or age brackets), we can set Category as a factor
# combining all the levels from our preprocessing.

all_levels <- c(
  levels(analysis_clean$age),
  levels(analysis_clean$gender),
  levels(analysis_clean$education),
  levels(analysis_clean$income),
  unique(analysis_clean$source) %>% na.omit() %>% as.character()
) %>% unique()

df_demo$Category <- factor(df_demo$Category, levels = all_levels)

p_demo <- ggplot(df_demo, aes(x = Category, y = n, fill = Category)) +
  geom_col(alpha = 0.9, width = 0.75, show.legend = FALSE) +
  facet_wrap(~ Demographic, scales = "free", ncol = 3) +
  labs(x = "", y = "Number of Users") +
  theme_minimal(base_size = 14, base_family = "sans") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 10, color = "#4a4a4a"),
    axis.text.y = element_text(size = 10, color = "#4a4a4a"),
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank(),
    strip.text = element_text(face = "bold", size = 13, color = "#1d3557", margin = margin(b = 10)),
    plot.background = element_rect(fill = "transparent", color = NA)
  ) +
  scale_fill_manual(values = colorRampPalette(prof_palette_1)(length(all_levels)))

ggplotly(p_demo, tooltip = c("x", "y")) %>% 
  config(displayModeBar = FALSE) %>%
  layout(margin = list(t = 30, b = 60, l = 20, r = 20), hovermode = "closest")
```

### Version 2 {layout-ncol="1"}

```{r}
#| echo: false
#| message: false
#| warning: false
#| title: "Age and Gender Pyramid"

df_pyramid <- analysis_clean |> 
  select(Age = age, Gender = gender) |> 
  drop_na(Age, Gender) |> 
  mutate(Age = fct_drop(Age)) |>
  count(Age, Gender) |> 
  mutate(
    n_pyramid = if_else(Gender == "Male", -n, as.numeric(n)),
    hover_text = paste("Gender: ", Gender, "<br>Count: ", n, sep = "")
  )

# Gender specific sleek palette
gender_palette <- c("Male" = "#3d5a80", "Female" = "#ee6c4d", "Non-binary" = "#98c1d9", "Prefer not to say" = "#e0fbfc")

p_pyramid <- ggplot(df_pyramid, aes(x = Age, y = n_pyramid, fill = Gender, text = hover_text)) +
  geom_col(alpha = 0.9, width = 0.8) +
  coord_flip() +
  scale_y_continuous(labels = abs) +
  theme_minimal(base_size = 14, base_family = "sans") +
  labs(x = "Age Group", y = "Number of Users") +
  theme(
    legend.position = "bottom",
    legend.title = element_blank(),
    panel.grid.minor = element_blank(),
    axis.text = element_text(color = "#4a4a4a")
  ) +
  scale_fill_manual(values = gender_palette)

ggplotly(p_pyramid, tooltip = "text") %>%
  layout(margin = list(b = 60), barmode = 'relative') %>%
  config(displayModeBar = FALSE)
```

```{r}
#| echo: false
#| message: false
#| warning: false
#| title: "Other Demographics"

df_demo_other <- analysis_clean |> 
  select(Region = source, Education = education, Income = income) |> 
  pivot_longer(everything(), names_to = "Demographic", values_to = "Category") |> 
  drop_na(Category) |> 
  count(Demographic, Category)

all_levels_other <- c(
  levels(analysis_clean$education),
  levels(analysis_clean$income),
  unique(analysis_clean$source) %>% na.omit() %>% as.character()
) %>% unique()

df_demo_other$Category <- factor(df_demo_other$Category, levels = all_levels_other)

other_palette <- c("#1d3557", "#457b9d", "#a8dadc", "#e63946", "#f1faee", "#2b9348", "#80b918", "#d2daca")

p_demo_other <- ggplot(df_demo_other, aes(x = Category, y = n, fill = Category)) +
  geom_col(alpha = 0.9, width = 0.75, show.legend = FALSE) +
  facet_wrap(~ Demographic, scales = "free", ncol = 3) +
  labs(x = "", y = "Number of Users") +
  theme_minimal(base_size = 14, base_family = "sans") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 10, color = "#4a4a4a"),
    axis.text.y = element_text(size = 10, color = "#4a4a4a"),
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank(),
    strip.text = element_text(face = "bold", size = 13, color = "#1d3557", margin = margin(b = 10))
  ) +
  scale_fill_manual(values = colorRampPalette(other_palette)(length(all_levels_other)))

ggplotly(p_demo_other, tooltip = c("x", "y")) %>% 
  config(displayModeBar = FALSE) %>%
  layout(margin = list(t = 30, b = 60, l = 20, r = 20), hovermode = "closest")
```

### Best Version {layout-ncol="1"}

```{r}
#| echo: false
#| message: false
#| warning: false
#| title: "Age and Gender Pyramid"

df_pyramid <- analysis_clean |> 
  select(Age = age, Gender = gender) |> 
  drop_na(Age, Gender) |> 
  mutate(Age = fct_drop(Age)) |>
  count(Age, Gender) |> 
  mutate(
    n_pyramid = if_else(Gender == "Male", -n, as.numeric(n)),
    hover_text = paste("Gender: ", Gender, "<br>Count: ", n, sep = "")
  )

# Gender specific sleek palette
gender_palette <- c("Male" = "#3d5a80", "Female" = "#ee6c4d", "Non-binary" = "#98c1d9", "Prefer not to say" = "#e0fbfc")

p_pyramid <- ggplot(df_pyramid, aes(x = Age, y = n_pyramid, fill = Gender, text = hover_text)) +
  geom_col(alpha = 0.9, width = 0.8) +
  coord_flip() +
  scale_y_continuous(labels = abs) +
  theme_minimal(base_size = 14, base_family = "sans") +
  labs(x = "Age Group", y = "Number of Users") +
  theme(
    legend.position = "bottom",
    legend.title = element_blank(),
    panel.grid.minor = element_blank(),
    axis.text = element_text(color = "#4a4a4a")
  ) +
  scale_fill_manual(values = gender_palette)

ggplotly(p_pyramid, tooltip = "text") %>%
  layout(margin = list(b = 60), barmode = 'relative') %>%
  config(displayModeBar = FALSE)
```

```{r}
#| echo: false
#| message: false
#| warning: false
#| title: "Region to Education to Income Flow"

# Define node sources
sankey_nodes <- unique(c(
  as.character(analysis_clean$source),
  as.character(analysis_clean$education),
  as.character(analysis_clean$income)
)) %>% na.omit()

# Define Links Region -> Education
links_region_edu <- analysis_clean %>%
  select(source = source, target = education) %>%
  drop_na() %>%
  count(source, target) %>%
  rename(value = n)

# Define Links Education -> Income
links_edu_inc <- analysis_clean %>%
  select(source = education, target = income) %>%
  drop_na() %>%
  count(source, target) %>%
  rename(value = n)

# Combine
sankey_links <- bind_rows(
  mutate(links_region_edu, source = as.character(source), target = as.character(target)),
  mutate(links_edu_inc, source = as.character(source), target = as.character(target))
) %>%
  mutate(
    source_id = match(source, sankey_nodes) - 1,
    target_id = match(target, sankey_nodes) - 1
  )

# Add matching colors
sankey_colors <- colorRampPalette(prof_palette_1)(length(sankey_nodes))

p_sankey <- plot_ly(
    type = "sankey",
    orientation = "h",
    node = list(
      label = sankey_nodes,
      pad = 15,
      thickness = 25,
      line = list(color = "#ffffff", width = 1),
      color = sankey_colors
    ),
    link = list(
      source = sankey_links$source_id,
      target = sankey_links$target_id,
      value = sankey_links$value,
      color = "rgba(100, 100, 100, 0.2)"
    )
  ) %>% 
  layout(
    margin = list(t = 30, b = 30, l = 30, r = 30),
    font = list(family = "sans", size = 12, color = "#4a4a4a")
  ) %>%
  config(displayModeBar = FALSE)

p_sankey
```

# Platform Behaviors

## Row {.tabset height="1000px"}

### Version 1 {layout-ncol="1"}

```{r}
#| echo: false
#| message: false
#| warning: false
#| title: "RedNote Usage Frequency"
df_rn <- analysis_clean |> 
  select(Response = rednote_now) |> 
  drop_na() |> 
  count(Response) |> 
  mutate(
    # Order responses on the x-axis
    Response = factor(Response, levels = c(
      "Multiple times a day", "Daily", "A few times per week", "Rarely"
    ))
  )

freq_palette <- c("Multiple times a day" = "#112A46", "Daily" = "#1A5276", "A few times per week" = "#5DADE2", "Rarely" = "#AED6F1")

p_comp <- ggplot(df_rn, aes(x = Response, y = n, fill = Response)) +
  geom_col(alpha = 0.95, width = 0.6) +
  labs(x = "", y = "Number of Users") +
  theme_minimal(base_size = 14, base_family = "sans") +
  theme(
    legend.position = "none",
    axis.text.x = element_text(angle = 45, hjust = 1, size = 11, color = "#2D2D2D"),
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank()
  ) +
  scale_fill_manual(values = freq_palette)

ggplotly(p_comp, tooltip = c("x", "y")) %>% 
  config(displayModeBar = FALSE) %>%
  layout(margin = list(t = 40, b = 80, l = 20, r = 20))
```

```{r}
#| echo: false
#| message: false
#| warning: false
#| title: "Primary Activities on RedNote"
# Process QID8
activities_df <- analysis_clean |> 
  select(qid8) |> 
  drop_na() |> 
  separate_longer_delim(qid8, delim = ",") |> 
  mutate(Activity = activities_dict[str_trim(qid8)]) |> 
  count(Activity, name = "n") |> 
  mutate(Activity = reorder(Activity, n))

act_palette <- c("#8e44ad", "#9b59b6", "#af7ac5", "#c39bd3", "#d7bde2")

p_act <- ggplot(activities_df, aes(x = Activity, y = n, fill = Activity)) +
  geom_col(alpha = 0.9, width = 0.7) +
  coord_flip() +
  labs(x = "", y = "Number of Selections", title = "What are users doing on RedNote?") +
  theme_minimal(base_size = 14, base_family = "sans") +
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 15, color = "#2c3e50"),
    panel.grid.major.y = element_blank(),
    panel.grid.minor = element_blank()
  ) +
  scale_fill_manual(values = colorRampPalette(act_palette)(length(unique(activities_df$Activity))))

ggplotly(p_act, tooltip = c("x", "y")) %>% 
  config(displayModeBar = FALSE) %>%
  layout(margin = list(t = 40, b = 20, l = 200, r = 20))
```

```{r}
#| echo: false
#| message: false
#| warning: false
#| title: "Reasons for Using RedNote"
# Process QID9
reasons_df <- analysis_clean |> 
  select(qid9) |> 
  drop_na() |> 
  separate_longer_delim(qid9, delim = ",") |> 
  mutate(Reason = reasons_dict[str_trim(qid9)]) |> 
  count(Reason, name = "n") |> 
  mutate(Reason = reorder(Reason, n))

reason_palette <- c("#b31237", "#e73e4b", "#f77f00", "#fcbf49", "#eae2b7")

p_reas <- ggplot(reasons_df, aes(x = Reason, y = n, fill = Reason)) +
  geom_col(alpha = 0.9, width = 0.75) +
  coord_flip() +
  labs(x = "", y = "Number of Selections", title = "Why are users moving to RedNote?") +
  theme_minimal(base_size = 14, base_family = "sans") +
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 15, color = "#2c3e50"),
    panel.grid.major.y = element_blank(),
    panel.grid.minor = element_blank()
  ) +
  scale_fill_manual(values = colorRampPalette(reason_palette)(length(unique(reasons_df$Reason))))

ggplotly(p_reas, tooltip = c("x", "y")) %>% 
  config(displayModeBar = FALSE) %>%
  layout(margin = list(t = 40, b = 20, l = 250, r = 20))
```

### Version 2 {layout-ncol="1"}

```{r}
#| echo: false
#| message: false
#| warning: false
#| title: "User Journey: Motivation to Activity to Frequency"

# Define mappings
activities_dict <- c("1" = "Browsing content", "2" = "Posting content", "3" = "Interacting with others", "4" = "Shopping", "5" = "Other Activity")
reasons_dict <- c("1" = "Similar US platforms unavailable", "2" = "Better content alignment", "3" = "Encouraged by friends/influencers", "4" = "Bypass U.S. restrictions", "5" = "Access unique products/services", "6" = "Curiosity about Chinese platforms", "7" = "Information outside US media", "8" = "Connect to international communities", "9" = "Other Reason")

# Expand data for Sankey
flow_df <- analysis_clean %>%
  select(id = qid1, qid9, qid8, Frequency = qid6) %>%
  drop_na() %>%
  separate_longer_delim(qid9, delim = ",") %>%
  mutate(Reason = reasons_dict[str_trim(qid9)]) %>%
  separate_longer_delim(qid8, delim = ",") %>%
  mutate(Activity = activities_dict[str_trim(qid8)]) %>%
  mutate(Frequency = factor(Frequency, levels = c(1, 2, 3, 4), labels = c("Rarely", "A few times per week", "Daily", "Multiple times a day")))

# Nodes
s_nodes <- unique(c(as.character(flow_df$Reason), as.character(flow_df$Activity), as.character(flow_df$Frequency))) %>% na.omit()

# Links
s_links <- bind_rows(
  flow_df %>% count(source = Reason, target = Activity) %>% rename(value = n),
  flow_df %>% count(source = Activity, target = as.character(Frequency)) %>% rename(value = n)
) %>%
  mutate(source_id = match(source, s_nodes) - 1, target_id = match(target, s_nodes) - 1)

# High-end palette for Sankey nodes
s_colors <- colorRampPalette(prof_palette_1)(length(s_nodes))

p_behavior_sankey <- plot_ly(
    type = "sankey",
    orientation = "h",
    node = list(
      label = s_nodes,
      pad = 15,
      thickness = 25,
      line = list(color = "#ffffff", width = 1),
      color = s_colors
    ),
    link = list(
      source = s_links$source_id,
      target = s_links$target_id,
      value = s_links$value,
      color = "rgba(100, 100, 100, 0.2)"
    )
  ) %>% 
  layout(
    margin = list(t = 30, b = 30, l = 30, r = 30),
    font = list(family = "sans", size = 11, color = "#4a4a4a")
  ) %>%
  config(displayModeBar = FALSE)

p_behavior_sankey
```

### Best Version

#### Row {height="55%"}

```{r}
#| echo: false
#| message: false
#| warning: false
#| title: "User Journey: Motivation to Activity to Frequency"

# Define mappings
activities_dict <- c("1" = "Browsing content", "2" = "Posting content", "3" = "Interacting with others", "4" = "Shopping", "5" = "Other Activity")
reasons_dict <- c("1" = "Similar US platforms unavailable", "2" = "Better content alignment", "3" = "Encouraged by friends/influencers", "4" = "Bypass U.S. restrictions", "5" = "Access unique products/services", "6" = "Curiosity about Chinese platforms", "7" = "Information outside US media", "8" = "Connect to international communities", "9" = "Other Reason")

# Expand data for Sankey
flow_df <- analysis_clean %>%
  select(id = qid1, qid9, qid8, Frequency = qid6) %>%
  drop_na() %>%
  separate_longer_delim(qid9, delim = ",") %>%
  mutate(Reason = reasons_dict[str_trim(qid9)]) %>%
  separate_longer_delim(qid8, delim = ",") %>%
  mutate(Activity = activities_dict[str_trim(qid8)]) %>%
  mutate(Frequency = factor(Frequency, levels = c(1, 2, 3, 4), labels = c("Rarely", "A few times per week", "Daily", "Multiple times a day")))

# Nodes
s_nodes <- unique(c(as.character(flow_df$Reason), as.character(flow_df$Activity), as.character(flow_df$Frequency))) %>% na.omit()

# Links
s_links <- bind_rows(
  flow_df %>% count(source = Reason, target = Activity) %>% rename(value = n),
  flow_df %>% count(source = Activity, target = as.character(Frequency)) %>% rename(value = n)
) %>%
  mutate(source_id = match(source, s_nodes) - 1, target_id = match(target, s_nodes) - 1)

# High-end palette for Sankey nodes
s_colors <- colorRampPalette(prof_palette_1)(length(s_nodes))

p_behavior_sankey_best <- plot_ly(
    type = "sankey",
    orientation = "h",
    node = list(
      label = s_nodes,
      pad = 15,
      thickness = 25,
      line = list(color = "#ffffff", width = 1),
      color = s_colors
    ),
    link = list(
      source = s_links$source_id,
      target = s_links$target_id,
      value = s_links$value,
      color = "rgba(120, 120, 120, 0.1)"  # Lighter and more transparent
    )
  ) %>% 
  layout(
    margin = list(t = 60, b = 30, l = 30, r = 30),
    font = list(family = "sans", size = 11, color = "#4a4a4a"),
    plot_bgcolor = "#ffffff",
    paper_bgcolor = "#ffffff",
    annotations = list(
      list(x = 0, y = 1.05, text = "Motivation", showarrow = FALSE, font = list(size = 14, color = "#1d3557", family="sans"), xref = "paper", yref = "paper"),
      list(x = 0.5, y = 1.05, text = "Activity", showarrow = FALSE, font = list(size = 14, color = "#1d3557", family="sans"), xref = "paper", yref = "paper"),
      list(x = 1, y = 1.05, text = "Usage Frequency", showarrow = FALSE, font = list(size = 14, color = "#1d3557", family="sans"), xref = "paper", yref = "paper")
    )
  ) %>%
  config(displayModeBar = FALSE)

p_behavior_sankey_best
```

#### Row {.tabset height="45%"}

```{r}
#| echo: false
#| message: false
#| warning: false
#| title: "Reasons for Using RedNote"
# Process QID9
reasons_df <- analysis_clean |> 
  select(qid9) |> 
  drop_na() |> 
  separate_longer_delim(qid9, delim = ",") |> 
  mutate(Reason = reasons_dict[str_trim(qid9)]) |> 
  count(Reason, name = "n") |> 
  mutate(Reason = reorder(Reason, n))

# Sankey-matched colors for Reasons nodes
reason_sankey_palette <- c(
  "Similar US platforms unavailable" = "#E87552",
  "Better content alignment" = "#264653",
  "Encouraged by friends/influencers" = "#B59269",
  "Bypass U.S. restrictions" = "#317874",
  "Access unique products/services" = "#93B27B",
  "Curiosity about Chinese platforms" = "#62A884",
  "Information outside US media" = "#DDC16C",
  "Connect to international communities" = "#F0B064",
  "Other Reason" = "#F0955D"
)

p_reas_best <- ggplot(reasons_df, aes(x = Reason, y = n, fill = Reason)) +
  geom_col(alpha = 0.9, width = 0.75) +
  coord_flip() +
  labs(x = "", y = "Number of Selections", title = "Why are users moving to RedNote?") +
  theme_minimal(base_size = 14, base_family = "sans") +
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 15, color = "#2c3e50"),
    panel.grid.major.y = element_blank(),
    panel.grid.minor = element_blank()
  ) +
  scale_fill_manual(values = reason_sankey_palette)

ggplotly(p_reas_best, tooltip = c("x", "y")) %>% 
  config(displayModeBar = FALSE) %>%
  layout(margin = list(t = 40, b = 20, l = 250, r = 20))
```

```{r}
#| echo: false
#| message: false
#| warning: false
#| title: "Primary Activities on RedNote"
# Process QID8
activities_df <- analysis_clean |> 
  select(qid8) |> 
  drop_na() |> 
  separate_longer_delim(qid8, delim = ",") |> 
  mutate(Activity = activities_dict[str_trim(qid8)]) |> 
  count(Activity, name = "n") |> 
  mutate(Activity = reorder(Activity, n))

# Sankey-matched colors for Activities nodes
act_sankey_palette <- c(
  "Browsing content" = "#9DA86C",
  "Posting content" = "#E48179",
  "Interacting with others" = "#BEA764",
  "Shopping" = "#D88A79",
  "Other Activity" = "#C98662"
)

p_act_best <- ggplot(activities_df, aes(x = Activity, y = n, fill = Activity)) +
  geom_col(alpha = 0.9, width = 0.7) +
  coord_flip() +
  labs(x = "", y = "Number of Selections", title = "What are users doing on RedNote?") +
  theme_minimal(base_size = 14, base_family = "sans") +
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 15, color = "#2c3e50"),
    panel.grid.major.y = element_blank(),
    panel.grid.minor = element_blank()
  ) +
  scale_fill_manual(values = act_sankey_palette)

ggplotly(p_act_best, tooltip = c("x", "y")) %>% 
  config(displayModeBar = FALSE) %>%
  layout(margin = list(t = 40, b = 20, l = 200, r = 20))
```

```{r}
#| echo: false
#| message: false
#| warning: false
#| title: "RedNote Usage Frequency"
df_rn <- analysis_clean |> 
  select(Response = rednote_now) |> 
  drop_na() |> 
  count(Response) |> 
  mutate(
    Response = factor(Response, levels = c(
      "Multiple times a day", "Daily", "A few times per week", "Rarely"
    ))
  )

# Sankey-matched colors for Frequency nodes
freq_sankey_palette <- c(
  "Rarely" = "#A5A973",
  "A few times per week" = "#F3B654",
  "Daily" = "#E7BFB7",
  "Multiple times a day" = "#9FA7A3"
)

p_comp_best <- ggplot(df_rn, aes(x = Response, y = n, fill = Response)) +
  geom_col(alpha = 0.95, width = 0.6) +
  labs(x = "", y = "Number of Users") +
  theme_minimal(base_size = 14, base_family = "sans") +
  theme(
    legend.position = "none",
    axis.text.x = element_text(angle = 45, hjust = 1, size = 11, color = "#2D2D2D"),
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank()
  ) +
  scale_fill_manual(values = freq_sankey_palette)

ggplotly(p_comp_best, tooltip = c("x", "y")) %>% 
  config(displayModeBar = FALSE) %>%
  layout(margin = list(t = 40, b = 80, l = 20, r = 20))
```

# Trust Analysis

## Row {.tabset height="600px"}

### Version 1 {layout-ncol="1"}

```{r}
#| echo: false
#| message: false
#| warning: false
#| title: "Privacy vs Trust Analysis"

df_scatter <- analysis_clean %>% drop_na(ethical_trust_diff, privacy_risk)
trust_palette_v1 <- c("Pro-China ethics" = "#956A88", "Pro-US ethics" = "#2A5196", "Equal trust" = "grey70")

p_scatter <- ggplot(df_scatter, aes(x = ethical_trust_diff, y = privacy_risk)) +
  geom_point(alpha = 0.8, size = 2.5, aes(color = trust_group, text = paste("Trust Diff:", ethical_trust_diff, "<br>Privacy Risk:", round(privacy_risk, 2)))) +
  geom_smooth(method = "lm", se = TRUE, color = "#333333", linewidth = 0.8, fill = "#e5e5e5") +
  scale_color_manual(values = trust_palette_v1) +
  labs(
    x = "Ethical Trust Difference (China − US)",
    y = "Perceived Privacy Risk",
    color = "Orientation"
  ) +
  theme_minimal(base_size = 14, base_family = "sans") +
  theme(
    legend.position = "none",
    panel.grid.minor = element_blank()
  )

ggplotly(p_scatter, tooltip = "text") %>%
  layout(margin = list(t = 40, b = 40, l = 50))
```

```{r}
#| echo: false
#| message: false
#| warning: false
#| title: "Trust Orientation Distribution"

df_hist <- analysis_clean %>% drop_na(ethical_trust_diff, trust_group)

p_hist <- ggplot(df_hist, aes(x = ethical_trust_diff, fill = trust_group)) +
  geom_histogram(bins = 20, color = "white", alpha = 0.9, linewidth = 0.5) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "#333333", linewidth = 1) +
  scale_fill_manual(values = trust_palette_v1) +
  labs(
    x = "Ethical Trust Difference (China − US)",
    y = "Respondents Count",
    fill = "Orientation"
  ) +
  theme_minimal(base_size = 14, base_family = "sans") +
  theme(
    legend.position = "right",
    panel.grid.minor = element_blank()
  )

ggplotly(p_hist) %>%
  layout(margin = list(t = 40, b = 40, l = 50))
```

### Version 2 {layout-ncol="1"}

```{r}
#| echo: false
#| message: false
#| warning: false
#| title: "Privacy vs Trust Analysis"

df_scatter <- analysis_clean %>% drop_na(ethical_trust_diff, privacy_risk)
trust_palette <- c("Pro-China ethics" = "#d62828", "Pro-US ethics" = "#003049", "Equal trust" = "#f77f00")

p_scatter_v2 <- ggplot(df_scatter, aes(x = ethical_trust_diff, y = privacy_risk)) +
  geom_point(alpha = 0.8, size = 2.5, aes(color = trust_group, text = paste("Trust Diff:", ethical_trust_diff, "<br>Privacy Risk:", round(privacy_risk, 2)))) +
  geom_smooth(method = "lm", se = TRUE, color = "#333333", linewidth = 0.8, fill = "#e5e5e5") +
  scale_color_manual(values = trust_palette) +
  labs(
    x = "Ethical Trust Difference (China − US)",
    y = "Perceived Privacy Risk",
    color = "Orientation"
  ) +
  theme_minimal(base_size = 14, base_family = "sans") +
  theme(
    legend.position = "none",
    panel.grid.minor = element_blank()
  )

ggplotly(p_scatter_v2, tooltip = "text") %>%
  layout(margin = list(t = 40, b = 40, l = 50))
```

```{r}
#| echo: false
#| message: false
#| warning: false
#| title: "Trust Orientation Distribution"

df_hist <- analysis_clean %>% drop_na(ethical_trust_diff, trust_group)

p_hist_v2 <- ggplot(df_hist, aes(x = ethical_trust_diff, fill = trust_group)) +
  geom_histogram(bins = 20, color = "white", alpha = 0.9, linewidth = 0.5) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "#333333", linewidth = 1) +
  scale_fill_manual(values = trust_palette) +
  labs(
    x = "Ethical Trust Difference (China − US)",
    y = "Respondents Count",
    fill = "Orientation"
  ) +
  theme_minimal(base_size = 14, base_family = "sans") +
  theme(
    legend.position = "right",
    panel.grid.minor = element_blank()
  )

ggplotly(p_hist_v2) %>%
  layout(margin = list(t = 40, b = 40, l = 50))
```

### Best Version {layout-ncol="1"}

```{r}
#| echo: false
#| message: false
#| warning: false
#| title: "Participants’ Ethical Trust Skews Toward China"

df_hist <- analysis_clean %>% drop_na(ethical_trust_diff, trust_group)

# Define the custom color palette requested by the user
best_trust_palette <- c("Pro-China ethics" = "#d62828", "Pro-US ethics" = "#003049", "Equal trust" = "grey70")

p_hist_best <- ggplot(df_hist, aes(x = ethical_trust_diff, fill = trust_group)) +
  geom_histogram(bins = 20, color = "white", alpha = 0.9, linewidth = 0.5) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "#333333", linewidth = 1) +
  scale_fill_manual(values = best_trust_palette) +
  labs(
    x = "Ethical Trust Difference (China − US)",
    y = "Respondents Count",
    fill = "Orientation",
    subtitle = "Higher values indicate stronger trust in Chinese platform ethics over US ones"
  ) +
  theme_minimal(base_size = 14, base_family = "sans") +
  theme(
    legend.position = "right",
    panel.grid.minor = element_blank()
  ) +
  annotate("text", x = 2, y = max(table(cut(df_hist$ethical_trust_diff, breaks=20))), 
           label = "Pro-China Trust", color = "#d62828", fontface = "bold", hjust = 0) +
  annotate("text", x = -2, y = max(table(cut(df_hist$ethical_trust_diff, breaks=20))), 
           label = "Pro-US Trust", color = "#003049", fontface = "bold", hjust = 1)

ggplotly(p_hist_best) %>%
  layout(margin = list(t = 40, b = 40, l = 50))
```

```{r}
#| echo: false
#| message: false
#| warning: false
#| title: "Higher Ethical Trust in China Corresponds to Lower Perceived Privacy Risk"

df_scatter <- analysis_clean %>% drop_na(ethical_trust_diff, privacy_risk)

p_scatter_best <- ggplot(df_scatter, aes(x = ethical_trust_diff, y = privacy_risk)) +
  geom_point(alpha = 0.8, size = 2.5, aes(color = trust_group, text = paste("Trust Diff:", ethical_trust_diff, "<br>Privacy Risk:", round(privacy_risk, 2)))) +
  geom_smooth(method = "lm", se = TRUE, color = "#333333", linewidth = 0.8, fill = "#e5e5e5") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "#888888") +
  scale_color_manual(values = best_trust_palette) +
  labs(
    x = "Ethical Trust Difference (China − US)",
    y = "Perceived Privacy Risk on RedNote",
    color = "Orientation",
    subtitle = "Negative correlation indicates users trusting American platforms are more wary of RedNote"
  ) +
  theme_minimal(base_size = 14, base_family = "sans") +
  theme(
    legend.position = "none",
    panel.grid.minor = element_blank()
  )

ggplotly(p_scatter_best, tooltip = "text") %>%
  layout(margin = list(t = 40, b = 40, l = 50))
```
